% Curriculum Vitae (CV)	
\documentclass[10pt,letterpaper,sans]{moderncv}

    \input{preamble}

\begin{document}

    \makecvtitle

\section{Overview}
\cvitem{Objective}{To continually enhance my expertise in computational science so as to accelerate development of reusable scientific software and maintain software infrastructure for high performance computing.}
%\cvitem{Objective}{To continually enhance scientific software development skills so as to consult on application development and assist in testing, tuning and deployment of applications in high performance computing workflows.}
\cvitem{Summary}{Extensive experience in computational physics across various domains including modeling, simulations and inverse problems. Skilled in scientific software engineering, parallel programming and management of software stacks on clusters.}

\section{Education}
    \input{nu}
    \input{madras}
    
\section{Professional Experience}
    \input{cody}

\section{Research Experience}
    \input{wave}
    \input{zp}
    \input{grapheneiitm}
%    \input{arci}
%    \input{grapheneiisc}
%    \input{grapheneiitb}
\newpage
\section{Teaching Experience}
    \input{physics}
    \input{python}

\section{Publications}
%\cvitem{2021}{{Fast X‐ray Nanotomography with Sub‐10 nm Resolution as a Powerful Imaging Tool for Nanotechnology and Energy Storage Applications} Vincent De Andrade, Viktor Nikitin, Michael Wojcik, Alex Deriy, Sunil Bean,  Deming Shu, Tim Mooney, Kevin Peterson, Prabhat Kc, Kenan Li, \textbf{Sajid Ali},  Kamel Fezzaa, Doga G\"{u}rsoy, Cassandra Arico, Saliha Ouendi, David Troadec,  Patrice Simon, Francesco De Carlo, and Christophe Lethien  \textit{Adv. Mater. 2021, 2008653}}
\cvitem{2020}{{Comparison of distributed memory algorithms for X-ray wave propagation in inhomogeneous media} \textbf{Sajid Ali}, Ming Du, Mark F. Adams, Barry Smith, and Chris Jacobsen  \textit{Optics Express Vol. 28, Issue 20, pp. 29590-29618} \textbf{Editor's pick}}
\cvitem{2020}{{Benchmark informed software upgrades on Quest, Northwestern’s HPC cluster} \textbf{Sajid Ali}, Alper Kinaci, and Alexander John Mamach  \textit{In Practice and Experience in Advanced Research Computing (PEARC '20), Association for Computing Machinery (526–529)}} 
\cvitem{2020}{{Tunable hard x-ray nanofocusing with Fresnel zone plates fabricated using deep etching} Kenan Li, \textbf{Sajid Ali}, Michael Wojcik, Vincent De Andrade, Xiaojing Huang, Hanfei Yan, Yong S. Chu, Evgeny Nazaretski, Ajith Pattammattel, and Chris Jacobsen  \textit{Optica Vol. 7, Issue 5, pp. 410-416}} 
\cvitem{2020}{{Effect of tilt on circular zone plate performance} \textbf{Sajid Ali} and Chris Jacobsen \textit{Journal of the Optical Society of America A Vol. 37, Issue 3, pp. 374-383 }} 
\cvitem{2018}{{Zone Plate Performance as a Function of Tilt Analyzed via Multislice Simulations} \textbf{Sajid Ali}, Kenan Li, Michael Wojcik and Chris Jacobsen \textit{Vol 24, Suppl. S2 (Proc. of the 14th Intl. Conf. on X-ray Microsc. 2018) pp. 298-299}} 
\cvitem{2016}{{Magnetism in intercalated graphene} \textbf{Sajid Ali}, BRK Nanda \textit{AIP Conference Proceedings 1731, 130040}} 

\section{Conference \& Workshops}
	\input{conferences}

\section{Professional Activities}
    \input{professional}

\section{Parallel \& Scientific Computing Skills}
	\input{computingskills}

%\section{Outreach, Volunteer and Leadership Experience}
%    \input{leadership}
    
\end{document}
